### 2020-04-22 final_report/data.tex
more edits to the autoencoder section

@@

Figure \cref{fig:var} shows the Matheron semivariance \cite{Matheron1963} for three discrete slices with coolant material varied, but all other discrete parameters fixed. Fits \cite{KrigingFig} to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.

@@

Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to feature extraction driven by neural
networks. Faced with many possible alternatives, we implemented a conventional
autoencoder, which relies on a three-layer network that is trained to replicate
the identity mapping. While it follows that the input and output layers of such
network are sized to accommodate the analysed dataset, the
hidden layer---also called the bottleneck---allows for variable number of
neurons that represent a smaller subspace. By scanning
over a range of bottleneck widths and investigating relative changes in the
validation loss, we assess the potential for dimensional reduction.

This approach was applied to two sets\footnote{Each set contained
\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples: (i) a subset of data obtained
from run~1 and (ii) a subset of a single slice obtained from run~2. Our
expectation was that while the former case would provide meaningful insights into
correlations within the feature space, the latter would validate our
autoencoder implementation by analysing a set of points that are trivially
reducible due to a number of fixed discrete features.

@@

Confirming our expectation that in the latter, trivially reducible case the
autoencoder should achieve greater dimensional reduction, we are inclined to
believe that our implementation is indeed efficient. However, we
must also conclude that in both examined cases this method failed to produce a
reduction that would be superior to a naïve approach.\footnote{In both tested cases we
	can trivially eliminate 7~dimensions due to overdetermined one-hot-encoded
	features and 2~dimensions due to sum-to-one constraints. Furthermore, in the
	single slice case we may omit 7~additional dimensions due to artificially fixed
features.} This supports the findings from PCA as well as the
presented semivariograms.

>>>>

% TODO: in results, we feature both Kriging and GPR with differing results -
% clarify their interchangeability here

@@

\Cref{fig:var} shows the Matheron semivariance \cite{Matheron1963} for three discrete slices with coolant material varied, but all other discrete parameters fixed. Fits \cite{KrigingFig} to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.

@@

Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to feature extraction driven by neural
networks. Faced with many possible alternatives, we implemented a conventional
autoencoder, which relies on a three-layer network that is trained to replicate
the identity mapping. While it follows that the input and output layers of such
network are sized to accommodate the analysed dataset, the
hidden layer, also called the bottleneck, allows for variable number of
neurons that represent a smaller subspace. By scanning
over a range of bottleneck widths and investigating relative changes in the
validation loss, we assess the potential for dimensional reduction.

In particular, we consider two equally-sized sets\footnote{Each set contained
\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples: (i) a subset of data obtained
from run~1 and (ii) a subset of a single slice obtained from run~2. Our
expectation was that while the former case would provide meaningful insights into
correlations within the feature space, the latter would validate our
autoencoder implementation by analysing a set of points that are trivially
reducible due to a number of fixed discrete features.

@@

Confirming our expectation that in the latter, trivially reducible case the
autoencoder should achieve greater dimensional reduction, we are inclined to
believe that our implementation is indeed operating as intended. However, we
must also conclude that in both examined cases this method failed to produce a
reduction that would be superior to a naïve approach.\footnote{In both tested cases we
	can trivially eliminate 7~dimensions due to overdetermined one-hot-encoded
	features and 2~dimensions due to sum-to-one constraints. Furthermore, in the
	single slice case we may omit 7~additional dimensions due to artificially fixed
features.} This is consistent with previous results obtained by PCA and kriging.
